---
title: "US Stock Market data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this page, we make dataset of US stock market using quantmod library and NASDAQ site.

Special thanks to following refernece.
https://github.com/hyunyulhenry/HenryQuant/blob/master/R/get_US_ticker.R


## Initial settings
```{r initalset}
rm(list=ls())
options(warn = -1) # suppressing warning message
options(install.packages.check.source = "no")

# Load multiple required packages at once
packages = c('quantmod')
suppressMessages(lapply(packages, require, character.only = T, quietly = TRUE)) 
## Character.only = T means elements in 'packages' can be assumed to be character stirngs.
```


First, we need to get symbols of all listed issues in US stock market from NASDAQ site.
(NYSE, NASDAQ, AMEX market)

we need to make function for downloading Symbol, name, sector and end prices of all listed issues. 

## Make 'get_US_symbol' function
```{r getsymbol function}
# This code is came from 'HenryQuant github'

get_US_symbol = function() {
  
  ## Following urls lead us to download each stock market's data
  url_NYSE = "http://www.nasdaq.com/screening/companies-by-name.aspx?letter=0&exchange=nyse&render=download"
  url_NASDAQ = "http://www.nasdaq.com/screening/companies-by-name.aspx?letter=0&exchange=nasdaq&render=download"
  url_AMEX = "http://www.nasdaq.com/screening/companies-by-name.aspx?letter=0&exchange=amexe&render=download"
  
  ## Download each file as csv type
  download.file(url_NYSE, destfile = "./url_NYSE.csv")
  download.file(url_NASDAQ, destfile = "./url_NASDAQ.csv")
  download.file(url_AMEX, destfile = "./url_AMEX.csv")
  
  ## Load each file
  NYSE = read.csv("./url_NYSE.csv", stringsAsFactors = F) ## 'stringsAsFactors = F' prevents columns with strings from being converted to factors
  NASDAQ = read.csv("./url_NASDAQ.csv", stringsAsFactors = F)
  AMEX = read.csv("./url_AMEX.csv", stringsAsFactors = F)
  
  
  ## Combine listed issues from three markets at one file
  us_symbol = rbind(NYSE, NASDAQ, AMEX)

  ## Data cleansing process
  us_symbol = us_symbol[us_symbol$MarketCap != "n/a", ]
  us_symbol = us_symbol[us_symbol$Sector != "n/a", ] 
  us_symbol = us_symbol[!duplicated(us_symbol$Name), ] # delete duplicated rows with respect to 'Name' 
  
  # Remove rownames of 'us_symbol'
  rownames(us_symbol) = NULL
  
  # Remove empty space in 'Symbol' using 'gsub(global substitute)' function
  us_symbol$Symbol = gsub(" ", "", us_symbol$Symbol)
  ## gsub function replaces "  " to "" in Symbol column
  
  # Remove 'IPO year' column
  us_symbol = us_symbol[, -c(5,8,9)]

  ## Saving results in csv file
  write.csv(us_symbol, "us_symbol.csv")
  
  
  ## Remove files
  file.remove("./url_NYSE.csv")
  file.remove("./url_NASDAQ.csv")
  file.remove("./url_AMEX.csv")
  
}
```

## Implements 'get_US_symbol' function and load csv file
```{r implement}

get_US_symbol()

us_stock = read.csv("us_symbol.csv", row.names = 1, stringsAsFactors = F)

# Show first 5 data
head(us_stock)
```

Now, using 'quantmod' library we make dataset containing financial indexes for each  stock.

## Use 'quantmod' package
```{r quntmod}
# Set various interested financial indexs in'indexes' vector with 'yahooQF' function
indexes = yahooQF(c("Price/Book", "P/E Ratio", "Price/EPS Estimate Next Year",
                             "Earning/Share", "Dividend Yield", 
                    "Market Capitalization", "Shares Outstanding", "Book Value",
                    "Earnings End Time", "Earnings Start Time"))
## We can see which indexes can be downloaded from 'getQuote' function through run yahooQF()

# Concatenate all symbols from us_stock data column 1 
codes = paste(us_stock[, 1], sep = "", collapse = ";") 

# Using 'getQuote' function to download financial indexes. 'indexes' and 'codes' are uese as arguments. 
Financial_indexes = getQuote(codes, what = indexes)

# Show first 5 results
head(Financial_indexes)

# Merge 'financial_indexes' with exisiting 'us_stock' dataset
us_stock = cbind(us_stock[, -4], Financial_indexes[, -1])


# Show first 5 results
head(us_stock)
```

## Save results
```{r save}
# Saving result as csv file
write.csv(us_stock, "us_stock.csv")
```



